---
title: "Flashpoint Analytics"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[Flashpoint](https://bluemaxima.org/flashpoint/) is a web-game preservation
project,made in 2018 in an effort to save as many games as possible from the
then upcoming Flash End-Of-Life, while also making them playable for everyone.
Today, it hosts more than 150 000 games and thousands of active users all around
the world.

This notebook contains a descriptive statistical analysis about the games
available in Flashpoint, with an emphasis on categorical data, such as the
technology that was used to make them or the publisher who used to host them in
the past.

The Flashpoint database, which keeps all the data that will be used in the
analysis, can be found [here](http://infinity.unstable.life/Flashpoint/Data/flashpoint.sqlite).

```{r import}
library(RSQLite)
library(dplyr)
```

## Retrieve Data

```{r retrieve}
dir.create("data")

# by default, there is a 60 seconds timeout limit when downloading a file
# this can be a problem when downloading large files, so we increase that limit

options(timeout = 300)

# download data from the source

url <- "http://infinity.unstable.life/Flashpoint/Data/flashpoint.sqlite"
destfile <- "data/flashpoint.sqlite"
download.file(url, destfile)

# connect to the database and store the "game" table in a dataframe

con <- dbConnect(SQLite(), "data/flashpoint.sqlite")
games <- dbReadTable(con, "game")
dbDisconnect(con)
```






```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
